A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2022-08-19 Analysis/models.Rmd
move file

write_rds(all_bootstrapped_predictions,"bootstrapped_GAM_predictions.rds")
write_rds(all_surprisal_predictions,"bootstrapped_GAM_surprisal_predictions.rds")

@@

#gam1 <- read_rds(here("Analysis/models/gam_predictions.rds")) %>%  
gam1 <- read_rds(here("Analysis/bootstrapped_GAM_surprisal_predictions.rds")) %>%  
  ggplot( aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
  #facet_grid(s~model, scales="free_y")+
  facet_grid(s~model)+
  coord_cartesian(xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

@@

N_replicates <- 101
res_ngram_spr <- gam_boot(ngram_mean_spr,spr_formula_interact,dats_for_prediction,N=N_replicates)
bootstrapped_gam_predictions_ngram_spr <- summarize_gam_boot_results(res_ngram_spr,dats_for_prediction,term_names,"5-gram")
res_grnn_spr <- gam_boot(grnn_mean_spr,spr_formula_interact,dats_for_prediction,N=N_replicates)
bootstrapped_gam_predictions_grnn_spr <- summarize_gam_boot_results(res_grnn_spr,dats_for_prediction,term_names,"GRNN")
res_txl_spr <- gam_boot(txl_mean_spr,spr_formula_interact,dats_for_prediction,N=N_replicates)
bootstrapped_gam_predictions_txl_spr <- summarize_gam_boot_results(res_txl_spr,dats_for_prediction,term_names,"Transformer-XL")
res_gpt_spr <- gam_boot(gpt_mean_spr,spr_formula_interact,dats_for_prediction,N=N_replicates)
bootstrapped_gam_predictions_gpt_spr <- summarize_gam_boot_results(res_gpt_spr,dats_for_prediction,term_names,"GPT-2")
all_bootstrapped_predictions_spr <- list(ngram=bootstrapped_gam_predictions_ngram_spr,
                                     grnn=bootstrapped_gam_predictions_grnn_spr,
                                     txl=bootstrapped_gam_predictions_txl_spr,
                                     gpt=bootstrapped_gam_predictions_gpt_spr)
write_rds(all_bootstrapped_predictions_spr,"bootstrapped_spr_GAM_predictions.rds")

term_conversions <- c("surp"="Current","past_surp"="Previous","past2_surp"="2Previous","past3_surp"="3Previous")
all_surprisal_predictions_spr <- rbind(rename(bootstrapped_gam_predictions_ngram_spr[[1]],surprisal=surp),
                                   rename(bootstrapped_gam_predictions_ngram_spr[[4]],surprisal=past_surp),
                                   rename(bootstrapped_gam_predictions_ngram_spr[[7]],surprisal=past2_surp),
                                   rename(bootstrapped_gam_predictions_ngram_spr[[10]],surprisal=past3_surp),
                                   rename(bootstrapped_gam_predictions_grnn_spr[[1]],surprisal=surp),
                                   rename(bootstrapped_gam_predictions_grnn_spr[[4]],surprisal=past_surp),
                                   rename(bootstrapped_gam_predictions_grnn_spr[[7]],surprisal=past2_surp),
                                   rename(bootstrapped_gam_predictions_grnn_spr[[10]],surprisal=past3_surp),
                                   rename(bootstrapped_gam_predictions_txl_spr[[1]],surprisal=surp),
                                   rename(bootstrapped_gam_predictions_txl_spr[[4]],surprisal=past_surp),
                                   rename(bootstrapped_gam_predictions_txl_spr[[7]],surprisal=past2_surp),
                                   rename(bootstrapped_gam_predictions_txl_spr[[10]],surprisal=past3_surp),
                                   rename(bootstrapped_gam_predictions_gpt_spr[[1]],surprisal=surp),
                                   rename(bootstrapped_gam_predictions_gpt_spr[[4]],surprisal=past_surp),
                                   rename(bootstrapped_gam_predictions_gpt_spr[[7]],surprisal=past2_surp),
                                   rename(bootstrapped_gam_predictions_gpt_spr[[10]],surprisal=past3_surp)
                                   ) %>%
  mutate(s=factor(term_conversions[term],levels=term_conversions)) %>%
  select(-term)
write_rds(all_surprisal_predictions_spr,"bootstrapped_spr_GAM_surprisal_predictions.rds")

@@

#gam1 <- read_rds(here("Analysis/models/spr_gam_predictions.rds")) %>%  
gam1 <- read_rds(here("Analysis/bootstrapped_spr_GAM_surprisal_predictions.rds")) %>%  
  ggplot( aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
  facet_grid(s~model)+
  coord_cartesian(xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

>>>>

write_rds(all_bootstrapped_predictions,here("Analysis/models/bootstrapped_GAM_predictions.rds"))
write_rds(all_surprisal_predictions,here("Analysis/models/bootstrapped_GAM_surprisal_predictions.rds"))

@@

#gam1 <- read_rds(here("Analysis/models/gam_predictions.rds")) %>%  
gam1 <- read_rds(here("Analysis/models/bootstrapped_GAM_surprisal_predictions.rds")) %>%  
  ggplot( aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
  #facet_grid(s~model, scales="free_y")+
  facet_grid(s~model)+
  coord_cartesian(xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

@@

N_replicates <- 101
res_ngram_spr <- gam_boot(ngram_mean_spr,spr_formula_interact,dats_for_prediction,N=N_replicates)
bootstrapped_gam_predictions_ngram_spr <- summarize_gam_boot_results(res_ngram_spr,dats_for_prediction,term_names,"5-gram")
res_grnn_spr <- gam_boot(grnn_mean_spr,spr_formula_interact,dats_for_prediction,N=N_replicates)
bootstrapped_gam_predictions_grnn_spr <- summarize_gam_boot_results(res_grnn_spr,dats_for_prediction,term_names,"GRNN")
res_txl_spr <- gam_boot(txl_mean_spr,spr_formula_interact,dats_for_prediction,N=N_replicates)
bootstrapped_gam_predictions_txl_spr <- summarize_gam_boot_results(res_txl_spr,dats_for_prediction,term_names,"Transformer-XL")
res_gpt_spr <- gam_boot(gpt_mean_spr,spr_formula_interact,dats_for_prediction,N=N_replicates)
bootstrapped_gam_predictions_gpt_spr <- summarize_gam_boot_results(res_gpt_spr,dats_for_prediction,term_names,"GPT-2")
all_bootstrapped_predictions_spr <- list(ngram=bootstrapped_gam_predictions_ngram_spr,
                                     grnn=bootstrapped_gam_predictions_grnn_spr,
                                     txl=bootstrapped_gam_predictions_txl_spr,
                                     gpt=bootstrapped_gam_predictions_gpt_spr)
write_rds(all_bootstrapped_predictions_spr,here("Analysis/models/bootstrapped_spr_GAM_predictions.rds"))

term_conversions <- c("surp"="Current","past_surp"="Previous","past2_surp"="2Previous","past3_surp"="3Previous")
all_surprisal_predictions_spr <- rbind(rename(bootstrapped_gam_predictions_ngram_spr[[1]],surprisal=surp),
                                   rename(bootstrapped_gam_predictions_ngram_spr[[4]],surprisal=past_surp),
                                   rename(bootstrapped_gam_predictions_ngram_spr[[7]],surprisal=past2_surp),
                                   rename(bootstrapped_gam_predictions_ngram_spr[[10]],surprisal=past3_surp),
                                   rename(bootstrapped_gam_predictions_grnn_spr[[1]],surprisal=surp),
                                   rename(bootstrapped_gam_predictions_grnn_spr[[4]],surprisal=past_surp),
                                   rename(bootstrapped_gam_predictions_grnn_spr[[7]],surprisal=past2_surp),
                                   rename(bootstrapped_gam_predictions_grnn_spr[[10]],surprisal=past3_surp),
                                   rename(bootstrapped_gam_predictions_txl_spr[[1]],surprisal=surp),
                                   rename(bootstrapped_gam_predictions_txl_spr[[4]],surprisal=past_surp),
                                   rename(bootstrapped_gam_predictions_txl_spr[[7]],surprisal=past2_surp),
                                   rename(bootstrapped_gam_predictions_txl_spr[[10]],surprisal=past3_surp),
                                   rename(bootstrapped_gam_predictions_gpt_spr[[1]],surprisal=surp),
                                   rename(bootstrapped_gam_predictions_gpt_spr[[4]],surprisal=past_surp),
                                   rename(bootstrapped_gam_predictions_gpt_spr[[7]],surprisal=past2_surp),
                                   rename(bootstrapped_gam_predictions_gpt_spr[[10]],surprisal=past3_surp)
                                   ) %>%
  mutate(s=factor(term_conversions[term],levels=term_conversions)) %>%
  select(-term)
write_rds(all_surprisal_predictions_spr,here("Analysis/models/bootstrapped_spr_GAM_surprisal_predictions.rds"))

@@

#gam1 <- read_rds(here("Analysis/models/spr_gam_predictions.rds")) %>%  
gam1 <- read_rds(here("Analysis/models/bootstrapped_spr_GAM_surprisal_predictions.rds")) %>%  
  ggplot( aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
  facet_grid(s~model)+
  coord_cartesian(xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

### 2022-08-19 Papers/Paper/manuscript.Rmd
move file

gam1 <- read_rds(here("Analysis/bootstrapped_GAM_surprisal_predictions.rds")) %>%  ggplot( aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
  #facet_grid(s~model, scales="free_y")+
  facet_grid(s~model)+
  coord_cartesian(xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Effect on Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

@@

```{r spr-gam, out.height="40%", fig.width=8, fig.height=4, fig.pos="ht", fig.cap="(ref:spr-gam-cap)"}
gam1 <- read_rds(here("Analysis/bootstrapped_spr_GAM_surprisal_predictions.rds")) %>%  ggplot( aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
  facet_grid(s~model)+
  coord_cartesian(xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Effect on Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

>>>>

gam1 <- read_rds(here("Analysis/models/bootstrapped_GAM_surprisal_predictions.rds")) %>%  ggplot( aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
  #facet_grid(s~model, scales="free_y")+
  facet_grid(s~model)+
  coord_cartesian(xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Effect on Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

@@

```{r spr-gam, out.height="40%", fig.width=8, fig.height=4, fig.pos="ht", fig.cap="(ref:spr-gam-cap)"}
gam1 <- read_rds(here("Analysis/models/bootstrapped_spr_GAM_surprisal_predictions.rds")) %>%  ggplot( aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
  facet_grid(s~model)+
  coord_cartesian(xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Effect on Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))
